---
title: "Creating POLAR3 and IMD Lookup"
output: html_document
---


```{r, echo=FALSE,warning=FALSE,eval=FALSE}
#setwd("/Users/alex/HE_Lookup/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/")
library(rgdal) #Shapefile functions
```

The first step is to import the [Office for National Statistics (ONS) postcode directory](http://www.ons.gov.uk/ons/guide-method/geography/products/postcode-directories/-nspp-/index.html) into R, which provides a lookup between postcodes and various nested zonal geography. Only those columns which are needed for this project are kept.

```{r eval=FALSE}
#Read a CSV file containing the ONS Postcode Directory
ONSPD_14 <- read.csv("Data/ONSPD_NOV_2014_UK.csv")

#Specify columns to keep
ONSPD_14 <- ONSPD_14[,c("pcd","oseast1m","osnrth1m","lsoa01","lsoa11","casward")]

#Remove records where there are blank caswards, LSOA or Easting and Northing
ONSPD_14 <- ONSPD_14[ONSPD_14$casward != "",]
ONSPD_14 <- ONSPD_14[ONSPD_14$lsoa01 != "",]
ONSPD_14 <- ONSPD_14[!is.na(ONSPD_14$oseast1m),]
ONSPD_14 <- ONSPD_14[!is.na(ONSPD_14$osnrth1m),]
```

The next step is to convert to Easting and Northing co-ordinates into latitude and longitude.

```{r eval=FALSE}
#setup CRS
ukgrid = "+init=epsg:27700"
latlong = "+init=epsg:4326"

# Create coordinates variable
coords <- cbind(Easting = as.numeric(as.character(ONSPD_14$oseast1m)),Northing = as.numeric(as.character(ONSPD_14$osnrth1m)))

# Create the SpatialPointsDataFrame
ONSPD_14_SP <- SpatialPointsDataFrame(coords, data = ONSPD_14, proj4string = CRS("+init=epsg:27700"))

# Convert from Eastings and Northings to Latitude and Longitude
ONSPD_14_SP_LL <- spTransform(ONSPD_14_SP, CRS(latlong))

# we also need to rename the columns
colnames(ONSPD_14_SP_LL@coords)[colnames(ONSPD_14_SP_LL@coords) == "Easting"] <- "Longitude"
colnames(ONSPD_14_SP_LL@coords)[colnames(ONSPD_14_SP_LL@coords) == "Northing"] <- "Latitude"
head(ONSPD_14_SP_LL@coords)

#Append onto ONSPD
ONSPD_14 <- cbind(ONSPD_14,ONSPD_14_SP_LL@coords)


```

#Index of Multiple Deprivation (IMD)

An Index of Multiple Deprivation is calculated for each constituent country of the UK. These rank areas (LSOA in [England](http://data.gov.uk/dataset/index-of-multiple-deprivation) and [Wales](http://gov.wales/statistics-and-research/welsh-index-multiple-deprivation-indicator-data/?lang=en), SOA in [Northern Ireland](http://www.nisra.gov.uk/deprivation/nimdm_2010.htm) and Data Zones in [Scotland](http://www.gov.scot/Topics/Statistics/SIMD/DataAnalysis/Background-Data-2012) ) by their relative deprivation. 

They are not comparable between counties, given the different geography, time periods, input data and methods. As such, each IMD is treated separately, with country specific deciles calculated. These data are then combined into a single data object that enables them to be appended onto the NSPD. All of the data were downloaded, however, converted to CSV. As a side note, it would be great if government agencies would **not release ``open'' data in proprietary formats!**

##IMD England

```{r eval=FALSE}
#Read IMD England
IMD_England <- read.csv("Data/England_IMD_Overall_2010.csv")

#Remove unwanted columns
IMD_England<- IMD_England[,c("LSOA_CODE","IMD_SCORE","IMD_RANK")]

#Create Deciles
IMD_England$Decile <- with(IMD_England, cut(IMD_England$IMD_SCORE, breaks=10, labels=10:1)) #1 = most deprived

#Create zone and length lookup
IMD_England$Zone <- "LSOA"
IMD_England$Zone_N <- nrow(IMD_England)

#Country Flag
IMD_England$CTRY <- "England"

#Year Flag
IMD_England$Year <- "2010"


```


##IMD Scotland

```{r eval=FALSE}
#Read IMD Scotland
IMD_Scotland <- read.csv("Data/Scotland_IMD_Overall_2012.csv")

#Create Deciles
IMD_Scotland$Decile <- with(IMD_Scotland, cut(IMD_Scotland$IMD_SCORE, breaks=10, labels=10:1)) #1 = most deprived

#Create zone and length lookup
IMD_Scotland$Zone <- "Data Zone"
IMD_Scotland$Zone_N <- nrow(IMD_Scotland)

#Country Flag
IMD_Scotland$CTRY <- "Scotland"

#Year Flag
IMD_Scotland$Year <- "2012"



```

##IMD Wales

```{r eval=FALSE}

#2011
# #Read IMD WALES
# IMD_Wales <- read.csv("Data/Wales_IMD_Overall_2011.csv")
# 
# #Read IMD WALES CORRECTIONS
# IMD_Wales_COR <- read.csv("Data/Wales_IMD_Overall_2011_CORRECTIONS.csv")
# 
# #Remove records with error
# IMD_Wales <- IMD_Wales[!IMD_Wales$LSOA_CODE %in% IMD_Wales_COR$LSOA_CODE,]
# 
# #Replace with corrections
# IMD_Wales <- rbind(IMD_Wales,IMD_Wales_COR)
# 
# #Create Deciles
# IMD_Wales$Decile <- with(IMD_Wales, cut(IMD_Wales$IMD_SCORE, breaks=10, labels=10:1)) #1 = most deprived

#2014
#Read IMD WALES
IMD_Wales <- read.csv("Data/Wales_IMD_Overall_2014.csv") #NB - Only supplies ranks

#Create Deciles
IMD_Wales$Decile <- with(IMD_Wales, cut(IMD_Wales$IMD_RANK, breaks=10, labels=1:10)) #1 = most deprived

#Create zone and length lookup
IMD_Wales$Zone <- "LSOA"
IMD_Wales$Zone_N <- nrow(IMD_Wales)

#Country Flag
IMD_Wales$CTRY <- "Wales"

#Year Flag
IMD_Wales$Year <- "2014"


```

##IMD Northern Ireland

```{r eval=FALSE}
#Read IMD Northern Ireland
IMD_NI <- read.csv("Data/Northern_Ireland_IMD_Overall_2010.csv")

#Create Deciles
IMD_NI$Decile <- with(IMD_NI, cut(IMD_NI$IMD_SCORE, breaks=10, labels=10:1)) #1 = most deprived

#Create zone and length lookup
IMD_NI$Zone <- "SOA"
IMD_NI$Zone_N <- nrow(IMD_NI)

#Country Flag
IMD_NI$CTRY <- "Northern Ireland"

#Year Flag
IMD_NI$Year <- "2010"

```

#Participation Of Local Areas Classification (POLAR)
The [POLAR classification](https://www.hefce.ac.uk/media/hefce/content/pubs/2012/201226/POLAR3.pdf) is compiled by HEFCE and presents a HE participation rate for Census Area Statistical Wards. This breaks young participation down into five quintiles (1=lowest rate; 5=highest rate)

```{r eval=FALSE}
#Read POLAR
POLAR <- read.csv("Data/casward_to_area_groups_12_09_10a.csv",skip=19)

#Remove unwanted columns
POLAR <- POLAR[,c("casward", "qYPR", "qAHE")]

#Remove trailing spaces
POLAR$casward <- gsub(" ","",POLAR$casward)

#Recode POLAR cats
library(plyr)

POLAR$POLAR_Y[POLAR$qYPR==1] <- "1st"
POLAR$POLAR_Y[POLAR$qYPR==2] <- "2nd"
POLAR$POLAR_Y[POLAR$qYPR==3] <- "3rd"
POLAR$POLAR_Y[POLAR$qYPR==4] <- "4th"
POLAR$POLAR_Y[POLAR$qYPR==5] <- "5th"

POLAR$POLAR_O[POLAR$qAHE==1] <- "1st"
POLAR$POLAR_O[POLAR$qAHE==2] <- "2nd"
POLAR$POLAR_O[POLAR$qAHE==3] <- "3rd"
POLAR$POLAR_O[POLAR$qAHE==4] <- "4th"
POLAR$POLAR_O[POLAR$qAHE==5] <- "5th"

POLAR <- POLAR[,-(2:3)]

```

#Creating a unified IMD table
Prior to merging the IMD tables onto the ONSPD the country files require unification into a single data frame object. Using the rbind function requires that the column names match, so these are all altered to mirror the England file.

```{r eval=FALSE}

#Add a NULL column for Wales
#IMD_Wales$IMD_SCORE <- NA
#IMD_Wales <- IMD_Wales[,c("LSOA_CODE","IMD_SCORE","IMD_RANK","Decile","Zone","Zone_N","CTRY", "Year")]

#Change names
colnames(IMD_England) <- c("CODE","IMD_SCORE","IMD_RANK","Decile","Zone","Zone_N","CTRY", "Year")
colnames(IMD_Scotland) <- c("CODE","IMD_SCORE","IMD_RANK","Decile","Zone","Zone_N","CTRY", "Year")
colnames(IMD_Wales) <- c("CODE","IMD_SCORE","IMD_RANK","Decile","Zone","Zone_N","CTRY", "Year")
colnames(IMD_NI) <- c("CODE","IMD_SCORE","IMD_RANK","Decile","Zone","Zone_N","CTRY", "Year")

#Create unified data frame (excluding Wales)
IMD_UK <- rbind(IMD_England,IMD_Scotland,IMD_NI)

```

#Merge ONSPD, POLAR and IMD lookups

The final stage is to merge the IMD and POLAR data onto the postcode directory, remove the postcode spaces and then export as a CSV file.

```{r eval=FALSE}
#POLAR
ONSPD_14 <- merge(ONSPD_14,POLAR, by.x="casward",by.y="casward", all.x=TRUE)

#IMD
ONSPD_14 <- merge(ONSPD_14,IMD_UK, by.x="lsoa01",by.y="CODE", all.x=TRUE)

#Extract Wales
ONSPD_14_NW <- ONSPD_14[!is.na(ONSPD_14$CTRY),]
ONSPD_14_W <- ONSPD_14[is.na(ONSPD_14$CTRY),]
ONSPD_14_W <- ONSPD_14_W[,-(11:17)]


#IMD Wales
ONSPD_14_W <- merge(ONSPD_14_W,IMD_Wales, by.x="lsoa11",by.y="CODE", all.x=TRUE)

#Bind Wales
ONSPD_14 <- rbind(ONSPD_14_NW,ONSPD_14_W)



#Remove E & N
ONSPD_14$oseast1m <- NULL
ONSPD_14$osnrth1m <- NULL

#Swap 2001 LSOA Codes in Wales for 2011 version
ONSPD_14$lsoa01 <- ifelse(ONSPD_14$CTRY == "Wales", as.character(ONSPD_14$lsoa11), as.character(ONSPD_14$lsoa01))

#Remove 2011 code
ONSPD_14$lsoa11 <- NULL

#Remove postcode spaces
ONSPD_14$pcd <- gsub(" ","",ONSPD_14$pcd)

#Write out CSV
write.csv(ONSPD_14,"ONSPD_14.csv",row.names=FALSE)

```


## Create zone geojson

For the mapping, a single polygon was required for each zone; including, LSOA, Data Zones, SOA and CAS Wards. As such, the following process creates directories of [geojson](http://geojson.org/) files that can be linked to a map.

* CAS Wards
    * [England](http://census.edina.ac.uk/easy_download_data.html?data=England_caswa_2001)
    * [Scotland](http://census.edina.ac.uk/easy_download_data.html?data=Scotland_caswa_2001)
    * [Wales](http://census.edina.ac.uk/easy_download_data.html?data=Wales_caswa_2001)
    * [Northern Ireland](http://census.edina.ac.uk/easy_download_data.html?data=Nireland_wa_2001)
* LSOA / DZ / SOA
    * [England](http://census.edina.ac.uk/easy_download_data.html?data=England_low_soa_2001)
    * [Scotland](http://sedsh127.sedsh.gov.uk/Atom_data/ScotGov/ZippedShapefiles/SG_DataZoneBdry_2001.zip)
    * [Wales](http://census.edina.ac.uk/easy_download_data.html?data=Wales_lsoa_2011)
    * [Northern Ireland](http://www.nisra.gov.uk/geography/SOA_.htm)


```{r eval=FALSE}
library(rgdal)
library(rgeos)
library(sp)
library(maptools)


#setup CRS
ukgrid = "+init=epsg:27700"
latlong = "+init=epsg:4326"


#CAS Wards (England)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
#setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/casward_2001/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")
#Read shapefile

polygon <- readOGR("shapefiles/", "England_caswa_2001_clipped")
#Remove unwanted
polygon <- polygon[,-(2:5)]

#ONS_CODE <- "00BYFJ"

WARD_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

for (x in 1:length(WARD_LIST)){
  
ONS_CODE <- WARD_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}




#CAS Wards (Wales)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
#setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")
#Read shapefile

polygon <- readOGR("shapefiles/", "Wales_caswa_2001_clipped")
#Remove unwanted
polygon <- polygon[,-c(1,3:4)]
colnames(polygon@data) <- "ONS_LABEL"

WARD_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/casward_2001")

for (x in 1:length(WARD_LIST)){
  
ONS_CODE <- WARD_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}

#CAS Wards (Northern Ireland)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
#setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")
#Read shapefile

polygon <- readOGR("shapefiles/", "NIreland_wa_2001_area")
#Remove unwanted
polygon <- polygon[,-1]
colnames(polygon@data) <- "ONS_LABEL"

WARD_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/casward_2001")

for (x in 1:length(WARD_LIST)){
  
ONS_CODE <- WARD_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}


#CAS Wards (Scotland)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
#setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")
#Read shapefile

polygon <- readOGR("shapefiles/", "Scotland_caswa_2001_area")
#Remove unwanted
polygon <- polygon[,-c(1,3:6)]
colnames(polygon@data) <- "ONS_LABEL"

WARD_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

setwd("/Volumes/Macintosh\ HD\ 2/Dropbox/projects/HE_Lookup/Boundaries/casward_2001")

for (x in 1214:length(WARD_LIST)){
  
ONS_CODE <- WARD_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(rep(ONS_CODE,length(polygonWGS@polygons)),row.names=names(polygonWGS))) #Convert back to spatial polygon data frame
colnames(polygonWGS@data) <- "ONS_LABEL"

polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(rep(ONS_CODE,length(polygonWGS@polygons)),row.names=names(polygonWGS))) #Convert back to spatial polygon data frame
colnames(polygonWGS@data) <- "ONS_LABEL"




#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}



############# LSOA / DZ / SOA



#LSOA (England)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")

#Read shapefile

polygon <- readOGR("shapefiles/", "england_low_soa_2001_gen")
#Remove unwanted
polygon <- polygon[,-(2:4)]
colnames(polygon@data) <- "ONS_LABEL"

SOA_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

for (x in 1:length(SOA_LIST)){
  
ONS_CODE <- SOA_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/LSOA_DZ_SOA")

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}



#DZ (Scotland)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")

#Read shapefile

polygon <- readOGR("shapefiles/", "SG_DataZone_Bdry_2001")
#Remove unwanted
polygon <- polygon[,-(2:6)]
colnames(polygon@data) <- "ONS_LABEL"

SOA_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

for (x in 1:length(SOA_LIST)){
  
ONS_CODE <- SOA_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/LSOA_DZ_SOA")

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}



#LSOA (Wales)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")

#Read shapefile

polygon <- readOGR("shapefiles/", "Wales_lsoa_2011_gen")
#Remove unwanted
polygon <- polygon[,-(2:4)]
colnames(polygon@data) <- "ONS_LABEL"

SOA_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

for (x in 1:length(SOA_LIST)){
  
ONS_CODE <- SOA_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/LSOA_DZ_SOA")

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}




#LSOA (NI)
#setwd("/Users/alex/HE_Lookup/Boundaries/")
setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/")

#Read shapefile

polygon <- readOGR("shapefiles/", "soa")
#Remove unwanted
polygon <- polygon[,-(1:3)]
colnames(polygon@data) <- "ONS_LABEL"

SOA_LIST <- unique(as.character(polygon@data$ONS_LABEL)) #unique is required to remove entries with multiple polygons

for (x in 1:length(SOA_LIST)){
  
ONS_CODE <- SOA_LIST[x]
  
polygonWGS <- spTransform(polygon[polygon@data$ONS_LABEL == ONS_CODE,], CRS(latlong)) #Set CRS
polygonWGS <- unionSpatialPolygons(polygonWGS,polygonWGS$ONS_LABEL) #Ensure a single polygon
polygonWGS <- gSimplify(polygonWGS, 0.0000009, topologyPreserve=TRUE) #Simplify
polygonWGS <- SpatialPolygonsDataFrame(polygonWGS,data=as.data.frame(ONS_CODE,row.names=names(polygonWGS))) #Convert back to spatial polygon data frame

setwd("/Users/alex/Dropbox/Projects/HE_Lookup/Boundaries/LSOA_DZ_SOA")

#Write file
writeOGR(polygonWGS, dsn=paste0(ONS_CODE,".geojson"), layer="polygonWGS", driver="GeoJSON")
remove(polygonWGS)
remove(ONS_CODE)

}


```

